Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-01 prop_letter.tex
prop_letter.tex \section{Theory} Added...

@@

@@

Formally, the expectation value of an observable with respect to an
IVPM should be the minimum and maximum expectation value of the same
observable with respect to states consistent with it. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space, whose definition is given as follow.

\begin{definition}$\bar{\mu}$ is called convex if for all commuting
$P_{0},P_{1}\in\events$, $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.\end{definition}

\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if it is the
minimal set satisfying the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \cup\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
\end{definition}

\noindent Having these two definitions, we can write down our idea
formally as follow.

\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.\end{thm}

@@

Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
when the space of events includes only mutually commuting sub-events.
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents experimenter know nothing about a coin before she tosses
it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
consistent with $\bar{\mu}_{2}$ on $\events_{0}$.

In general, although measurements done with limited resources and
poor precision may not uniquely identify the true state of a classical
system, there is always at least one system that is consistent with
the measurements.

>>>>

\section{Theory}

@@

Quantum IVPMs turns into the classical IVPMs setup~\cite{JamisonLodwick2004}
when the space of events includes only mutually commuting sub-events,
where $\events'\subseteq\events$ is called a sub-event space if it
satisfies the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on $\events_{0}$,
$\bar{\mu}_{1}|_{\events_{0}}$, gives a classical IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the density matrices~$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents experimenter know nothing about a coin before she tosses
it, and two classical states~$\proj{0}$ and $\proj{1}$ are both
consistent with $\bar{\mu}_{2}$ on $\events_{0}$.

In general, although measurements done with limited resources and
poor precision may not uniquely identify the true state of a classical
system, when the system satisfies an extra-condition called convex,
there is always at least one system that is consistent with the measurements.

\begin{definition}
$\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{definition}

@@

Formally, the expectation value of an observable with respect to an
IVPM should be the minimum and maximum expectation value of the same
observable with respect to states consistent with it. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space induced by an observable.

\begin{definition}
Given an observable~$\mathbf{O}$ with its spectrum decomposition~(\ref{eq:spectrum-decomposition}).
A set of projectors~$\events'\subseteq\events$ is called a sub-event
space induced by $\mathbf{O}$ if it is the minimal sub-event space
satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
\end{definition}

\noindent Having this definitions, we can write down our idea formally
as follow.

\begin{thm}
Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.
\end{thm}

\newpage{}

@@
